Solving the Shallow Water Equations\\ using Finite Volumes and Lax-Friedrichs

### 2017-12-23 paper/paper.tex
Attractive code listings

\newtcblisting{my_julia}[1][]{%
  listing engine=minted,
  minted language=julia,
  minted options={breaklines,breakanywhere,fontsize=\scriptsize,gobble=8},
  listing only,
  before skip=0pt,
  after skip=8pt,
  left skip=0pt,
  right skip=0pt,
  size=fbox,
  sharp corners,
  %colframe=white!75!black,
  colframe=white,
  boxrule=0pt,
  frame hidden,
  #1
}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% standard IEEE bibliography style from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/supported/IEEEtran/bibtex
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{IEEEabrv,../references}

\input{appendix}

>>>>

% Patch to fix https://github.com/T-F-S/tcolorbox/issues/12
\makeatletter
\def\tcb@minted@input@listing#1#2#3#4{%
  \edef\temp@a{#4}%
  \ifx\temp@a\@empty%
  \else%
    \toks@=\expandafter{#4}%
    \edef\tcb@temp{\noexpand\usemintedstyle{\the\toks@}}%
    \tcb@temp%
  \fi%
  \toks@=\expandafter{#1}%
  \edef\tcb@temp{\noexpand\inputminted[\the\toks@]}%
  \IfFileExists{\minted@outputdir#3}%
    {\tcb@temp{#2}{\minted@outputdir#3}}%
    {\tcb@temp{#2}{#3}}%
}
\makeatother

\newtcblisting{myjulia}{%
  listing engine=minted,
  minted language=julia,
  minted options={fontsize=\scriptsize,firstnumber=last,linenos},
  listing only,
  before skip=0pt,
  after skip=8pt,
  left skip=0pt,
  right skip=0pt,
  size=fbox,
  rounded corners,
  colframe=white!75!black,
  boxrule=0pt,
  frame hidden,
  width=\linewidth - 1em
}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% standard IEEE bibliography style from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/supported/IEEEtran/bibtex
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{IEEEabrv,../references}
\newpage
\input{appendix3}
